\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2016-04-07 paper/paper.tex
temp commit
added some more description to results, probably needs more, but my mind is kind of blank atm

%------------------------------------------------
\section{Results}
\label{results}
%% TODO %%
% Give and describe results
%%
% Table for results can be found at appendices
The measured computation times are visualized in \autoref{fig:basiconly} and \autoref{fig:fastonly}, the actual times can be found in \autoref{table:measurements}.

\subsection{Basic Algorithm}
\autoref{fig:basiconly} shows the measure computation times of the basic color refinement algorithm for the three paths graphs of sizes 5 through 5120. The larger sizes of this graph

@@

@@

%------------------------------------------------
\section{Discussion} %Change section name?
\label{disc}
%% TODO %%
% Describe the effectiveness of the algorithms on various types of graphs, and examine the differences
%%

>>>>

%------------------------------------------------
\section{Results}
\label{results}
%% WIP %%
% Give and describe results
%%
% Table for results can be found at appendices
The measured computation times are visualized in \autoref{fig:basiconly} and \autoref{fig:fastonly}, the actual times can be found in \autoref{table:measurements}.

\subsection{Basic Algorithm}
\autoref{fig:basiconly} shows the measured computation times of the basic color refinement algorithm for the three paths graphs of sizes 5 through 5120. The larger sizes of this graph would have taken too long to compute within reasonable time.

@@

\subsection{Fast Algorithm}
\autoref{fig:fastonly} shows the measured computation times of the fast color refinement algorithm for the three paths graphs of sizes 5 through 20480. Larger variants of the graph were not available and therefore not used.

@@

%------------------------------------------------
\section{Discussion} %Change section name?
\label{disc}
%% WIP %%
% Describe the effectiveness of the algorithms on various types of graphs, and examine the differences
%%
